\documentclass[11pt,a4paperm,sans]{moderncv}

% Age calc
\newcounter{Age}
\newcommand{\WhichAge}[3]{\setcounter{Age}{\numexpr(\month-#2)*100+\day-#3}%
   \ifnum\value{Age}<0%
      \setcounter{Age}{\numexpr\year-#1-1}%
   \else%
      \setcounter{Age}{\numexpr\year-#1}%
   \fi%
   \theAge}

%moderncvthemes are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman'
% (for roman fonts, instead of sans serif fonts)
\moderncvtheme[red]{casual}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.8]{geometry}
% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% only for the classic theme, if you want to change the width
% of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}

% required when changes are made to page layout lengths
\AtBeginDocument{\recomputelengths}

% personal data
\firstname{Andrey}
\familyname{Cherkashin}
\title{Software Engineer}
\mobile{+1.805.280.9169}
%\phone{phone (optional)}
%\fax{fax (optional)}
\email{andoriyu@gmail.com}
\homepage{github.com/andoriyu}
%\photo[64pt]{picture}
%\quote{\WhichAge{1989}{11}{11} years old.}

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------

\begin{document}
\maketitle

\section{Education}
\cventry{2007--2011}{B.S.}{Siberian Federal University}{Krasnoyarsk, Russian Federation}{\textit{System Analysis, and Management}}{}
\cventry{2012--2014}{M.S.}{Siberian Federal University}{Krasnoyarsk, Russian Federation}{\textit{System Analysis in Enterprise Management}}{}
\cventry{2009-2011}{English Classes}{Santa Barbara City College}{Santa Barbara, CA}{}{}

\section{Technologies}
\cvline{Languages}{Java, Ruby, Javascript, Objective C, Rust, Kotlin, Python}
\cvline{Frameworks}{Spring MVC, Akka, Ruby On Rails, Cocoa, OTP, React (Native)}
\cvline{Op.\ systems}{FreeBSD, GNU/Linux, macOS}
\cvline{Databases}{PostgreSQL, Cassandra, MySQL, CouchDB, ElasticSearch}
\cvline{Cloud}{Amazon Web Services, Kubernetes, Docker, Google Cloud Platform}
\cvline{Other}{Salt, Nginx, \LaTeX{}, ZSH}

\section{Languages}
\cvlanguage{Russian}{Native}{}
\cvlanguage{English}{Excellent}{}

\section{Relevant Coursework}
\subsection{Siberian Federal University}
\cvline{B.S.}{Methods of optimizing staff schedule in retail stores}
\cvline{M.S.}{Developing customer loyalty program in retail stores}

\section{Open Source}
\subsection{FreeBSD}
\cvline{}{
  \begin{itemize}
    \item Port maintainer:
      \begin{itemize}
        \item Various JetBrains IDEs
        \item Various sysutils written in rust
        \item Maintaning stable and nightly builds of Rust
      \end{itemize}
  \end{itemize}
}
\subsection{Rust}
\cvline{}{
  \begin{itemize}
    \item Maintained stage0 of rustc until automatic builds were implemented
    \item Hoop
      \begin{itemize}
        \item Fast ring buffer
      \end{itemize}
    \item libZetta
      \begin{itemize}
        \item Safe Rust interface to ZFS administrative tools
      \end{itemize}
    \item cargo-suity
      \begin{itemize}
        \item CI friendly JUnit reporter for cargo
      \end{itemize}
  \end{itemize}
}

\section{Experience}
\subsection{FabFitFun Inc}
\cventry{2018--current}{Senior Engineer}{FabFitFun Inc.}{Los Angeles, CA}{}{}
\cvline{}{
  \begin{itemize}
    \item Responsibilities and Achievements:
      \begin{itemize}
        \item Refactored local development environment with docker. (Make, Docker)
        \item Refactored test suits to work with docker and Circle CI. (Docker)
        \item Implemented pipeline to generate seed data for local development environment. (Docker, MySQL, sh, Make)
        \item Managing custom IAM roles and policies. (AWS)
        \item Responsible for CI/CD pipeline development and maintenance. (Jenkins, Kubernetes, Argo)
        \item Implemented "infrastructure as a code" for all environments. (Terraform, Vault)
      \end{itemize}
    \item Technologies used: MySQL, Amazon Web Services, Kubernetes, Jenkins, Terraform.
  \end{itemize}
}
\subsection{Flipagram}
\cventry{2013--2018}{Senior Backend Engineer}{Flipagram}{Los Angeles, CA}{}{}
\cvline{}{
  \begin{itemize}
    \item Responsibilities and Achievements:
      \begin{itemize}
        \item Development of internal administrative tools for social network. (Java, Ruby, PostgreSQL)
        \item Supporting mobile client teams by implementing features on backend. (Java, PostgreSQL)
        \item Reposible for internal music catalog infrastructure development and maintenance. (Java, PostgreSQL, Spark)
        \item Administrative interface to internal music catalog. (Ruby, Java)
        \item Engineered ingestion pipeline for internal music catalog with support for multiple content providers. (Spring Batch, Spark)
        \item Engineered content policy engine to be compliant with music licenses. (Java, ZooKeeper)
      \end{itemize}
    \item Technologies used: Spring MVC, Ruby on Rails, Cassandra, Amazon Web Services, Docker
    \item Worked on: Platform Backend, Internal Admin Tools, Content Moderation System, Music Platform Backend
    \item Other Responsibilities: Running daily standups
  \end{itemize}
}
\subsection{Cheerful Inc.}
\cventry{2012--2013}{Full Stack Engineer}{Cheerful Inc.}{Culver City, CA}{}{}
\cvline{}{
  \begin{itemize}
    \item Technologies used: Spring MVC, Python, CocoaTouch, Amazon Web Services
    \item Worked on: Front end, Internal Admin Tools, iOS application
    \item Responsibilities:
      \begin{itemize}
        \item Development of internal administrative tools for social network. (Python, Java, MongoDB)
        \item Turning PSDs into actual web pages. (Python, Javascript)
        \item Making front-end work in all browsers (even Internet Explorer 7) (Javascript)
      \end{itemize}
  \end{itemize}
}
\subsection{KF Sinrah}
\cventry{2007--2009}{Director of IT}{KF Sinrah}{Krasnoyarsk, Russian Federation}{}{IT Consulting}
\subsection{Freelance}
\cventry{2009--2017}{Software Developer}{Freelansim}{}{}{}

\section{Projects}

\subsection{Vocational}
\cventry{2012--2013}{RADOS Monitoring}{iOS application}{Tablet application for mining equipment monitoring service}{}{}{}
\cvline{}{Development of mobile dashboard and administrative interface for iOS devices.}
\cventry{2011--2013}{Sibrados}{Management, and analytics system for mining equipment}{}{}{}{}{}
\cvline{}{Development of complex monitoring solution for mining equipment.}
\cvline{}{
  \begin{itemize}
    \item Responsibilities:
      \begin{itemize}
        \item Setup up local network infrastructure and servers. (Chef, FreeBSD, IPSec)
        \item Oversee development of embedded monitor nodes. (C, FreeBSD)
        \item Design and implement field data collection system. (C, Erlang)
      \end{itemize}
    \item Technologies used:
      \begin{itemize}
        \item Backend: Spring MVC, Riak, PostgreSQL, Java, ElasticSearch, RabbitMQ, DTrace
        \item Monitoring node: Embedded C, Erlang (field data collector)
        \item Administrative interface and dashboard: Ruby on Rails, Backbone.js, D3.js
      \end{itemize}
  \end{itemize}
}

\cventry{2010--2011}{Razvivaika}{iOS Game}{Russian alphabet game for kids}{}{http:/itunes.apple.com/us/app/id405879674?mt=8}{}
  \cvline{}{\begin{itemize}
    \item Technologies used:
      \begin{itemize}
        \item Objective-C, CocoaTouch
      \end{itemize}
  \end{itemize}
}

\cventry{2012}{SibRados}{Corporate Website}{http://sibrados.com}{}{}{}{}
\cvline{}{Ruby on Rails}

%\section{Personal information}
%\cvline{Age}{26}
%\cvline{Marital status}{single}
%\cvline{Kids}{no}

\end{document}
